Challenges in Developing Great MCQMC Software

### 2022-07-14 MCQMC_2022_ChallengesDevelopSoftware.tex
Office Computer Updates

\thanksnote{with input from Mark Klinchin, the GAIL an QMCPy teams, and  friends \\
	partially supported by SigOpt, an Intel company \\[2ex]
	Please join us Tuesday, July 19, for lunch at ??? \\ to discuss the future of MCQMC software \\[2ex]
	Thanks to the organizers as we meet again in person\\
	Slides at  \href{??}{\nolinkurl{speakerdeck.com/fjhickernell/quasi-monte-carlo-software}}
}
\event{MCQMC 2022, Linz}
\date[]{July 18, 2022}

@@

\begin{frame}{Next Steps}
	content...
\end{frame}

>>>>

\thanksnote{with input from Mark Klinchin, the GAIL an QMCPy teams, and  friends \\
	partially supported by SigOpt, an Intel company \\[2ex]
	Please join us Tuesday, July 19, at 12:45 PM for lunch at Bella Casa \\ to discuss the future of MCQMC software \\[2ex]
	Thanks to the organizers as we meet again in person\\
	Slides at  \href{??}{\nolinkurl{speakerdeck.com/fjhickernell/quasi-monte-carlo-software}}
}
\event{MCQMC 2022, Linz}
\date[]{July 18, 2022}

@@

\begin{frame}{Next Steps}
	\includegraphics[width=0.5\textwidth]{ProgramsImages/PizeriaBellaCasa.png}
\end{frame}
